\chapter{Foreward}

We have all wondered what it means to exist. What are we? Who are we? What other rhetorical questions
can I ask? It was on a chill March day in the two thousandth and twentieth year following the birth of Christ
that I found myself in solitude along a lake. It's often these moments of solitude that lead the most riveting
thoughts. When walking alone in the woods beside a lake you are reminded of how you are, after all, just a 
meatbag with a consciousness wobbling along in space.

When coming to this realization, many (or rather most) humans turn to religion to give them meaning. While
an understandable decision, I don't believe it is a satisfying answer. After all, there are dozens of religions
in the world, and each one of them is so confident that they are the right religion that they go to war over
it.

Alas, this book is not meant to bash religion by any means. In fact, I am religious myself. The point of
this book is to instead offer a different, more logical and philosphical warrant for valuing existance, and
why without first understanding existance we cannot truly value anything.

\pagebreak

After all, there are two possible scenerios we could have ended up in. Only one of them is a reality:

\begin{enumerate}
    \item We don't have any physical existence
    \item We do have physical existence
\end{enumerate}

The first is utterly useless. After all, when talking about really enything, existence has to be guaranteed
before all. Otherwise, no conversation is worth anything.

The latter of the two is of course the only one from which we can draw conclusions. Before we even begin
to talk about anything, we must first guarantee and ensure the latter of the two scenerios I put forth. Indeed, nothing
makes sense until we first actualize our existance. This is where this book begins.